### 2019-03-12 paper/sex_selection_spacing-ver2.tex
Begin editing high education results

@@

When trying to understand the strength of son preference, it is interesting
that the sex ratio is also statistically significantly different
from the natural rate in the case where women already have one
son for the third and fourth spells.
Again, the sex ratio in the presence of one son for the third and
fourth spells are higher in urban areas than rural areas, although
the difference is less than for women with only girls.
Hence, it is possible that women are still willing to use sex selection
even after giving birth to one, although this behavior may also 
be in response to either experienced
or expected mortality of the first son born.

It also appears that there is a slightly elevated sex ratio among 
first-born for urban women. 
There is, however, no corresponding increase in spacing; instead,
the median duration has fallen over time and is the lowest among
the three education groups.
Hence, unless duration between marriage and first birth has decreased 
substantially by itself, for example, because of improved health, it
is not clear how much stock to place on the increased sex ratio
among first-borns as evidence for sex selection among first-borns.

Both of the last two results are different from prior studies using NFHS data.
There are two potential explanations.
First, the NFHS-4 is substantially larger than the three prior surveys.
Hence, it is possible that the effects have been there all along, but 
we did not have the power to detect them.
Second, it is possible that at least the first-born results are an
artifact of any recall error not captured by the data restrictions.
Certain types of recall error would also explain why the sex ratio for
the second spell and one boy is statistically significantly \emph{below} 
the natural sex ratio.

>>>>

Women with eight or more years of education are those expected to have the lowest 
fertility and the highest use of sex selection based on the prior literature.
Figure \ref{fig:bootstrap_high} shows that not only do this group, indeed, have lower 
fertility than the two prior groups, it is also falling rapidly over time.
Of women with one birth, the probability of having a second birth when the first-born
is a son is only around 70 percent for urban women and around 80 percent for rural women,
and for those with a first-born daughter it is around 80 percent for urban women and 90 
percent for rural women.
The falling fertility is even more clear for the third and fourth spells when the woman
has given birth to at least one son.
At the beginning of the sample, urban women with at least one boy had a close to 75
percent likelihood of having a birth, but that has fallen to only around 25 percent.
However, son preference still shows clearly in the parity progression probability for 
women without a son, with the decline for the third and fourth spell substantially
slower for both urban and rural women without a son than for those with at least one son.

@@

When trying to understand the strength of son preference, it is interesting
that the sex ratio is also statistically significantly different
from the natural rate in the case where women already have one
son for the third and fourth spells.
Again, the sex ratio in the presence of one son for the third and
fourth spells are higher in urban areas than rural areas, although
the difference is less than for women with only girls.
Hence, it is possible that women are still willing to use sex selection
even after giving birth to one, although this behavior may also 
be in response to either experienced
or expected mortality of the first son born.
This result is different from prior studies using NFHS data.
The NFHS-4 sample is substantially larger than the three prior surveys.
Hence, it is possible that the effect has been there all along, but 
we did not have the power to detect it.
